Supplemental Material for submission ``Do Objects in Real-World Images Have a Canonical Name?''

### 2019-05-21 papers/EMNLP2019/analysis.tex
better refs on variation in image captioning

%As type counts give a rather rough indication for variation in object naming, 
Next, we look at the following agreement measures, computed with $t=1$: % to assess agreement on the object names:
{\small
\begin{itemize}
\setlength{\itemsep}{0pt}
\setlength{\parskip}{0pt}
\item \textbf{\% top}: the average relative frequency of the most frequent response (shown in percent)
\item \textbf{$H$}: the $H$ agreement measure from \citet{snodgrass}, where 0 is perfect agreement: \mbox{$H = \sum_{i=1}^k p_i~log_2\frac{1}{p_i}$}, 
where $k$\ denotes the number of name types and $p_i$\ is the proportion of name type\ $i$ in the responses.% \cs{@Sina: right?}
\item \textbf{N}: the average number of types in the response set of ManyNames
\item \textbf{top=VG}: the percentage of items where the top response in ManyNames is the \vg name 
\item \textbf{\% VG}: the average relative frequency of the \vg name in the response set 
\end{itemize}
}
%\cs{Maybe it would be good to give an example for the class-level, to make it easier to follow the results discussion}
%Again, we measure instance-level and class-level agreement on response sets for objects and synset classes, respectively.
%o account for potential noise\cs{redundant}, we filter out names with a frequency of\ 1 from the response sets.

As shown in Table\ \ref{tab:agree}, generally, the agreement measures follow a similar pattern as the type counts discussed in Section\ \ref{subsec:counts}:
On the instance level, %our annotators achieve a fair amount of overlap in their object naming choices, with 
the most frequent name accounts for 75\%\  and the \vg name for 63\% of the responses on average. On the class level, however, the agreement is much lower: The average frequency of the top name drops to\ 56\% and that of the \vg name even to\ 23\%. The $H$ measures indicate a fair amount of agreement for instances, a bit lower than the agreement found in picture norming studies on artificial images (e.g.\ \newcite{snodgrass} report an average $H$ of 0.55). On the class-level, again, an average $H$ value of 2 points to a much more even distribution of name frequencies.

>>>>

%As type counts give a rather rough indication for variation in object naming, 
Next, we look at the following agreement measures, computed with $t=1$: % to assess agreement on the object names:
\begin{itemize}
\setlength{\itemsep}{0pt}
\setlength{\parskip}{0pt}
\item \textbf{\% top}: the average relative frequency of the most frequent response (shown in percent)
\item \textbf{$H$}: the $H$ agreement measure from \citet{snodgrass}, where 0 is perfect agreement: \mbox{$H = \sum_{i=1}^k p_i~log_2\frac{1}{p_i}$}, 
where $k$\ denotes the number of name types and $p_i$\ is the proportion of name type\ $i$ in the responses.% \cs{@Sina: right?}
\item \textbf{N}: the average number of types in the response set of ManyNames
\item \textbf{top=VG}: the percentage of items where the top response in ManyNames is the \vg name 
\item \textbf{\% VG}: the average relative frequency of the \vg name in the response set 
\end{itemize}

%\cs{Maybe it would be good to give an example for the class-level, to make it easier to follow the results discussion}
%Again, we measure instance-level and class-level agreement on response sets for objects and synset classes, respectively.
%o account for potential noise\cs{redundant}, we filter out names with a frequency of\ 1 from the response sets.

Table\ \ref{tab:agree} shows, generally, that the agreement measures follow a similar pattern as the type counts in Section\ \ref{subsec:counts}:
On the instance level, %our annotators achieve a fair amount of overlap in their object naming choices, with 
the most frequent name accounts for 75\%\  and the \vg name for 63\% of the responses on average. On the class level, the agreement is much lower: The average frequency of the top name drops to\ 56\% and that of the \vg name even to\ 23\%. The $H$ measures indicate a fair amount of agreement for instances, which is a bit lower than in picture norming studies on artificial images (e.g.\ \newcite{snodgrass} report an average $H$ of 0.55). On the class-level, again, an average $H$ value of 2 points to a much more even distribution of name frequencies.
